Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-08-13 paper/paper.results.tex
Complete LP vs historical comparison

In order to evaluate the generated schedule and compare it with the manually created schedule, we outline the adherence of each schedule to the constraints presented in table \ref{tbl:constraint-summary}. As we can see from table \ref{tbl:constraints-comparison}, the optimal schedule generated using the software was able to satisfy all mandatory constraints. On the other hand, we can see that the manually created schedule was not able to satisfy all mandatory constraints. In particular, we see that it assigned clinicians to multiple consecutive blocks for all four years. Moreover, the manual schedule did not have an equal distribution of weekends and holidays for all four years of data. Evaluating the objectives, we see that [...\textit{request conflicts}]. Moreover, the manual schedule does not attempt to align weekend assignments adjacent to block assignments.

>>>>

In order to evaluate the generated schedule and compare it with the manually created schedule, we outline the adherence of each schedule to the constraints presented in table \ref{tbl:constraint-summary}. As we can see from table \ref{tbl:constraints-comparison}, the optimal schedule generated using the software was able to satisfy all mandatory constraints. On the other hand, we can see that the manually created schedule was not able to satisfy all mandatory constraints. In particular, we see that it assigned clinicians to multiple consecutive blocks for all four years. Moreover, the manual schedule did not have an equal distribution of weekends and holidays for all four years of data. Evaluating the objectives, we see that LP outperforms the manually created schedule in all four years, by accommodating almost all time-off requests and ensuring that weekends are always assigned close to blocks.
